```{r}
#| label: setup
#| include: false

library(beepr)
library(cffr)
library(codemetar)
library(groomr)
library(here)
library(readr)
library(rutils) # https://github.com/danielvartan/rutils
library(stringr)
```

# groomr

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/danielvartan/groomr/workflows/R-CMD-check/badge.svg)](https://github.com/danielvartan/groomr/actions)
[![Codecov test coverage](https://codecov.io/gh/danielvartan/groomr/branch/main/graph/badge.svg)](https://app.codecov.io/gh/danielvartan/groomr?branch=main)
[![License: MIT](https://img.shields.io/badge/license-MIT-green)](https://choosealicense.com/licenses/mit/)
[![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-2.1-4baaaa.svg)](code_of_conduct.md)
<!-- badges: end -->

## Overview

`groomr` is an R package that helps you tidy strings and text files.

## Installation

You can install `groomr` using the [`remotes`](https://github.com/r-lib/remotes) package:

``` {r}
#| eval: false

remotes::install_github("danielvartan/groomr")
```

## Usage

Here are some functions that you can use with `groomr`:

- `blank_line_neighbours()`: Identify blank lines around a line.
- `cutter()`: Cut a vector into pieces.
- `normalize_hashtags()`: Normalize hashtags in text files.
- `remove_blank_line_dups()`: Remove duplicate blank lines in text files.
- `replace_pattern()`: Replace a pattern in text files.
- `split_by_pattern`: Split a character vector by a pattern.
- `split_file()`: Split text files into multiple files.

Click [here](https://danielvartan.github.io/groomr/) to see the full list of functions.

## Contributing

We welcome contributions, including bug reports. Take a moment to review our [Guidelines for Contributing](https://danielvartan.github.io/groomr/CONTRIBUTING.html).

## License

[![License:
MIT](https://img.shields.io/badge/license-MIT-green)](https://opensource.org/license/mit/)

`groomr` code is released under the [MIT license](https://opensource.org/license/mit/).

<br>

Become an `groomr` supporter!

Click [here](https://github.com/sponsors/danielvartan) to make a donation. Please indicate the `groomr` package in your donation message.
