# groomr <a href = "https://danielvartan.github.io/groomr/"><img src = "man/figures/logo.svg" align="right" width="120" /></a>

<!-- quarto render -->

```{r}
#| label: setup
#| include: false

library(groomr)

library(badger)
library(beepr)
library(cffr)
library(codemetar)
library(groomr) # https://github.com/danielvartan/groomr
library(here)
library(rutils) # https://github.com/danielvartan/rutils

badge_codecov() |> invisible() # To avoid unnecessary messages.
```

<!-- badges: start -->
```{r}
#| echo: false
#| output: asis

cat(
  badge_repostatus("active"),
  badge_github_actions(action = "R-CMD-check.yaml"),
  badge_codecov(),
  badge_license(
    license = "GPLv3",
    color = "bd0000",
    url = "https://www.gnu.org/licenses/gpl-3.0",
    alt = "GNU GPLv3 License"
  ),
  badge_custom(
    x = "Contributor%20Covenant",
    y = "3.0",
    color = "4baaaa",
    url = "https://www.contributor-covenant.org/version/3/0/code_of_conduct/",
    alt = "Contributor Covenant 3.0 Code of Conduct"
  )
)
```
<!-- badges: end -->

## Overview

`groomr` is an R package designed to help you tidy and organize R objects and files. It provides functions for cleaning, renaming, splitting, and managing files and data, making workflows more efficient and reproducible.

> If you find this project useful, please consider giving it a star! &nbsp; [![GitHub repo stars](https://img.shields.io/github/stars/danielvartan/groomr)](https://github.com/danielvartan/groomr/)

## Installation

You can install `groomr` using the [`remotes`](https://github.com/r-lib/remotes) package:

```r
# install.packages("remotes")
remotes::install_github("danielvartan/groomr")
```

## Usage

Here are some functions that you can use with `groomr`:

- [`make_machine_readable()`](https://danielvartan.github.io/groomr/reference/make_machine_readable.html): Make a string machine-readable.
- [`normalize_names()`](https://danielvartan.github.io/groomr/reference/normalize_names.html): Make file and directory names machine-readable.
- [`remove_blank_line_dups()`](https://danielvartan.github.io/groomr/reference/remove_blank_line_dups.html): Remove blank lines duplicates in files.
- [`replace_in_file()`](https://danielvartan.github.io/groomr/reference/replace_in_file.html): Replace a pattern in files.
- [`sort_files_by_size()`](https://danielvartan.github.io/groomr/reference/sort_files_by_size.html): Sort files based on their size.
- [`split_by_pattern()`](https://danielvartan.github.io/groomr/reference/split_by_pattern.html): Split a character vector by a pattern.
- [`split_file()`](https://danielvartan.github.io/groomr/reference/split_file.html): Split a single file into `n` parts.
- [`split_files_by_size()`](https://danielvartan.github.io/groomr/reference/split_files_by_size.html): Split files based on their size.
- [`to_title_case_pt()`](https://danielvartan.github.io/groomr/reference/to_title_case_pt.html): Convert to title case considering Portuguese rules.
- [`zip_files_by_pattern()`](https://danielvartan.github.io/groomr/reference/zip_files_by_pattern.html): Zip files by a pattern.

Click [here](https://danielvartan.github.io/groomr/) to see the full list.

## License

```{r}
#| echo: false
#| output: asis

cat(
  badge_license(
    license = "GPLv3",
    color = "bd0000",
    url = "https://www.gnu.org/licenses/gpl-3.0",
    alt = "GNU GPLv3 License"
  )
)
```

```text
Copyright (C) 2026 Daniel Vartanian

groomr is free software: you can redistribute it and/or modify it under the
terms of the GNU General Public License as published by the Free Software
Foundation, either version 3 of the License, or (at your option) any later
version.

This program is distributed in the hope that it will be useful, but WITHOUT ANY
WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A
PARTICULAR PURPOSE. See the GNU General Public License for more details.

You should have received a copy of the GNU General Public License along with
this program. If not, see <https://www.gnu.org/licenses/>.
```

## Contributing

```{r}
#| echo: false
#| output: asis

cat(
  badge_custom(
    x = "Contributor%20Covenant",
    y = "3.0",
    color = "4baaaa",
    url = "https://www.contributor-covenant.org/version/3/0/code_of_conduct/",
    alt = "Contributor Covenant 3.0 Code of Conduct"
  )
)
```

Contributions are always welcome! Whether you want to report bugs, suggest new features, or help improve the code or documentation, your input makes a difference.

Before opening a new issue, please check the [issues tab](https://github.com/danielvartan/groomr/issues) to see if your topic has already been reported.